---
title: "Line Breaks"
format: html
editor: visual
---

## Testing Line Breaks output

Line breaks not being rendered correctly in a PDF is a known issue. We will skip the quarto rendered PDF and evaluate the line break behavior in other output options.

The example table evaluates line breaks in: - Title - Column Headers - Table Header - Cells

```{r eval=FALSE}

library(gtsummary)
tbl <- gtsummary::tbl_summary(gtsummary::trial, by = trt, include = c(age, grade), missing = "always", label = list(age = "Age  \n\nlinebreak in a cell")) |> add_overall()|>
   modify_header(all_stat_cols() ~ "**{level}**\n\n N = {n}")

  gt_table <- tbl$table_body |> 
  gt::gt(caption = gt::md("This is the caption  \n\n[Used for cross referencing in Quarto]")) |> 
  gt::fmt_markdown(columns = label) |> # need this to recognize the line break in the table body
  # Column headers with line breaks
  gt::cols_label(
    stat_0 = gt::md("**Overall**"),
    stat_1 = gt::md("**Drug A**  \n\nManual Line Break"), 
    stat_2 = gt::md("**Drug B**  \n\nManual Line Break")
  ) |> 
  gt::tab_header(gt::md("This is the Title  \n\nwith a linebreak"), subtitle = "This is the Subtitle")
  

gt::gtsave(gt_table, filename = "outputs/docx/linebreaks_gt_word.docx")
```

### gt_save PDF

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/pdf/linebreaks_gt_pdf.pdf")
```

[Preview the Output](outputs/pdf/linebreaks_gt_pdf.pdf)
- manual linebreaks work
- title linebreaks work
- linebreak in a cell works

### rmarkdown rendered PDF

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/pdf/linebreaks_rmd_pdf.pdf)

- title linebreaks work
- manual linebreak works but disrupts cell alignment
- linebreak in a cell doesn't work

### gt_save rendered word file

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/docx/linebreaks_gt_word.docx")
```

[Preview the Output](outputs/docx/linebreaks_gt_word.docx)
- title linebreak not working
- cell linebreak not working
- manual linebreaks work

### quarto rendered word file

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/docx/linebreaks_qmd_word.docx)

- title linebreak not working
- cell linebreak not working
- manual linebreaks work

### rmarkdown rendered word file

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/docx/linebreaks_rmd_word.docx)

- title linebreak not working
- cell linebreak not working
- manual linebreaks work
