---
title: "Line Breaks"
format: html
editor: visual
---

Line breaks not being rendered correctly in a PDF is a known issue. We will skip the quarto rendered PDF and evaluate the line break behavior in other output options.

The example table evaluates line breaks in:

-   Title

-   Column Headers

-   Table Headers

-   Cells

```{r eval=FALSE}
library(gtsummary)
tbl <- gtsummary::tbl_summary(gtsummary::trial, by = trt, include = c(age, grade), missing = "always", label = list(age = "Age  \n\U00A0\U00A0linebreak in a cell")) |> add_overall()
gt_table <- tbl$table_body |> 
  gt::gt(caption = gt::md("This is the caption  \n[Used for cross referencing in Quarto]")) |> 
  gt::fmt_markdown(columns = label) |> # need this to recognize the line break in the table body
  # Column headers with line breaks
  gt::cols_label(
    stat_0 = gt::md("**Overall**"),
    stat_1 = gt::md("**Drug A**  \nManual Line Break"), 
    stat_2 = gt::md("**Drug B**  \nManual Line Break")
  ) |> 
  gt::tab_header(gt::md("This is the Title  \nwith a linebreak"), subtitle = "This is the Subtitle")
```

### gt_save PDF

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/pdf/linebreaks_gt_pdf2.pdf")
```

###### Preview the Output

![](outputs/pdf/linebreaks_gt_pdf.pdf){width="80%" height="1000"}

|     | Date       | Finding                    |
|-----|------------|----------------------------|
| 1   | 06/19/2025 | manual linebreaks work     |
| 2   | 06/19/2025 | title linebreaks work      |
| 3   | 06/19/2025 | linebreaks in a cell works |

### rmarkdown rendered PDF

```{r eval = FALSE}
gt_table
```

###### Preview the Output

![](outputs/pdf/linebreaks_rmd_pdf.pdf){width="80%" height="1000"}

|     | Date       | Finding                                            |
|-----|------------|----------------------------------------------------|
| 1   | 06/19/2025 | title linebreaks work                              |
| 2   | 06/19/2025 | manual linebreak works but disrupts cell alignment |
| 3   | 06/19/2025 | linebreak in a cell doesn't work                   |

### gt_save rendered word file

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/docx/linebreaks_gt_word.docx")
# converting word to pdf locally 
doconv::docx2pdf("outputs/docx/linebreaks_gt_word.docx")
```

###### Preview the Output

![](outputs/docx/linebreaks_gt_word.pdf){width="80%" height="1000"}

|     | Date       | Finding                     |
|-----|------------|-----------------------------|
| 1   | 06/19/2025 | title linebreak not working |
| 2   | 06/19/2025 | cell linebreak not working  |
| 3   | 06/19/2025 | manual linebreaks work      |

### quarto rendered word file

```{r eval = FALSE}
gt_table
# converting word to pdf locally 
doconv::docx2pdf("outputs/docx/linebreaks_qmd_word.docx")
```

###### Preview the Output

![](outputs/docx/linebreaks_qmd_word.pdf){width="80%" height="1000"}

|     | Date       | Finding                     |
|-----|------------|-----------------------------|
| 1   | 06/19/2025 | title linebreak not working |
| 2   | 06/19/2025 | cell linebreak not working  |
| 3   | 06/19/2025 | manual linebreaks work      |

### rmarkdown rendered word file

```{r eval = FALSE}
gt_table
# converting word to pdf locally 
doconv::docx2pdf("outputs/docx/linebreaks_rmd_word.docx")
```

###### Preview the Output

![](outputs/docx/linebreaks_rmd_word.pdf){width="80%" height="1000"}

|     | Date       | Finding                     |
|-----|------------|-----------------------------|
| 1   | 06/19/2025 | title linebreak not working |
| 2   | 06/19/2025 | cell linebreak not working  |
| 3   | 06/19/2025 | manual linebreaks work      |
