---
title: "Indentation"
format: html
editor: visual
---

The example table evaluates Indentation.

```{r}
library(gtsummary)
tbl <- gtsummary::tbl_summary(gtsummary::trial, by = trt, include = c(age, grade), missing = "always", label = list(age = "Age")) |> add_overall()

gt_table <- tbl$table_body |> 
  gt::gt(caption = gt::md("This is the caption")) |> 
  gt::fmt_markdown(columns = label) |> 
  gt::cols_hide(columns = c(variable, var_type, row_type, var_label)) |> 
  gt::sub_missing(missing_text = "") |> 
  # Indentation
  gt::text_transform(
    locations = gt::cells_body(columns = label, rows = !row_type %in% "label"),
    fn = function(x) paste0(strrep("\U00A0", times = 2), x)
  ) |> 
  gt::text_transform(
    locations = gt::cells_body(columns = label, rows = row_type %in% "missing"),
    fn = function(x) paste0(strrep("\U00A0", times = 4), x)
  ) 
```

### gt_save PDF

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/pdf/indentations_gt_pdf.pdf")
```

###### Preview the Output

![](outputs/pdf/indentations_gt_pdf.pdf){width="80%" height="1000"}

|     | Date       | Finding   |
|-----|------------|-----------|
| 1   | 06/19/2025 | no issues |

### rmarkdown rendered PDF

```{r eval = FALSE}
gt_table
```

###### Preview the Output

![](outputs/pdf/indentation_rmd_pdf.pdf){width="80%" height="1000"}

|     | Date       | Finding   |
|-----|------------|-----------|
| 1   | 06/19/2025 | no issues |

### gt_save rendered word file

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/docx/indentation_gt_word.docx")
# converting word to pdf locally 
doconv::docx2pdf("outputs/docx/indentation_gt_word.docx")
```

###### Preview the Output

![](outputs/docx/indentation_gt_word.docx){width="80%" height="1000"}

|     | Date       | Finding                              |
|-----|------------|--------------------------------------|
| 1   | 06/19/2025 | cell contents replaced with xml code |

```{html}
# <md_container><w:p><w:pPr></w:pPr><w:r><w:rPr></w:rPr><w:t xml:space="preserve">Unknown</w:t></w:r></w:p></md_container>
```

### quarto rendered word file

```{r eval = FALSE}
gt_table
# converting word to pdf locally 
doconv::docx2pdf("outputs/docx/indentation_qmd_word.docx")
```

###### Preview the Output

|     | Date       | Finding                |
|-----|------------|------------------------|
| 1   | 06/19/2025 | No indentation applied |

### rmarkdown rendered word file

```{r eval = FALSE}
gt_table
# converting word to pdf locally 
doconv::docx2pdf("outputs/docx/indentation_rmd_word.docx")
```

###### Preview the Output

![](outputs/docx/indentation_rmd_word.pdf){width="80%" height="1000"}

|     | Date       | Finding                              |
|-----|------------|--------------------------------------|
| 1   | 06/19/2025 | cell contents replaced with xml code |
