---
title: "Source Notes"
format: html
editor: visual
---

## Testing Source Note output

```{r}
library(gtsummary)

tbl <- gtsummary::tbl_summary(gtsummary::trial, by = trt, include = c(age, grade), missing = "always", label = list(age = "Age")) |> add_overall()

gt_table <- tbl$table_body |> 
  gt::gt(caption = gt::md("This is the caption")) |> 
  #source notes
  gt::tab_source_note("This is Source Note 1") |> 
  gt::tab_source_note("This is Source Note 2") |> 
  gt::tab_source_note("Abbreviations: Q1 = First Quartile; Q3 = Third Quartile")
```

### gt_save PDF

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/pdf/source_notes_gt_pdf.pdf")
```
###### Preview the Output
![](outputs/pdf/footnotes_gt_pdf.pdf){width=80% height=1000}
- no issues

### rmarkdown rendered PDF
```{r eval = FALSE}
gt_table
```
###### Preview the Output
![](outputs/pdf/source_notes_rmd_pdf.pdf){width=80% height=1000}
-   no issues

### gt_save rendered word file

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/docx/source_notes_gt_word.docx")
```
###### Preview the Output
![](outputs/docx/source_notes_gt_word.docx){width=80% height=1000}
-   no issues

### quarto rendered word file

```{r eval = FALSE}
gt_table
```
###### Preview the Output
![](outputs/docx/source_notes_qmd_word.docx){width=80% height=1000}
-   no issues

### rmarkdown rendered word file

```{r eval = FALSE}
gt_table
```
###### Preview the Output
![](outputs/docx/source_notes_rmd_word.docx){width=80% height=1000}
-   no issues
