---
title: "Table Too Wide"
format: html
editor: visual
---

## Testing output when the table is too long

```{r eval=FALSE}
library(gtsummary)
library(dplyr)

set.seed(123)
data <- tibble(
  id = 1:100,
  age = sample(18:90, 100, replace = TRUE),
  sex = sample(c("Male", "Female"), 100, replace = TRUE),
  race = sample(c("White", "Black", "Asian", "Hispanic"), 100, replace = TRUE),
  bmi = round(runif(100, 18, 35), 1),
  smoking_status = sample(c("Never", "Former", "Current"), 100, replace = TRUE),
  diabetes = sample(c("Yes", "No"), 100, replace = TRUE),
  hypertension = sample(c("Yes", "No"), 100, replace = TRUE),
  heart_disease = sample(c("Yes", "No"), 100, replace = TRUE),
  cancer = sample(c("Yes", "No"), 100, replace = TRUE),
  cholesterol = sample(c("Normal", "High"), 100, replace = TRUE),
  exercise_frequency = sample(0:7, 100, replace = TRUE),
  alcohol_intake = sample(c("None", "Low", "Moderate", "High"), 100, replace = TRUE),
  family_history = sample(c("Yes", "No"), 100, replace = TRUE),
  education = sample(c("High School", "College", "Graduate", "Post-Grad", "Middle School", "Elementary School", "Pre School", "Kindergarten"), 100, replace = TRUE),
  marital_status = sample(c("Single", "Married", "Divorced"), 100, replace = TRUE),
  employment_status = sample(c("Employed", "Unemployed", "Retired"), 100, replace = TRUE),
  region = sample(c("North", "South", "East", "West"), 100, replace = TRUE),
  health_insurance = sample(c("Yes", "No"), 100, replace = TRUE),
  medication = sample(c("Yes", "No"), 100, replace = TRUE),
  visits_last_year = sample(0:10, 100, replace = TRUE),
  satisfaction = sample(1:5, 100, replace = TRUE)
)

# Create a wide summary table
summary_table <- data %>%
  tbl_summary(
    by = education,
    statistic = list(all_continuous() ~ "{mean} ({sd})", 
                     all_categorical() ~ "{n} ({p}%)"),
    label = list(
      age ~ "Age (years)",
      bmi ~ "BMI",
      smoking_status ~ "Smoking Status",
      diabetes ~ "Diabetes",
      hypertension ~ "Hypertension",
      heart_disease ~ "Heart Disease",
      cancer ~ "Cancer",
      cholesterol ~ "Cholesterol",
      exercise_frequency ~ "Exercise Frequency (days/week)",
      alcohol_intake ~ "Alcohol Intake",
      family_history ~ "Family History",
      marital_status ~ "Marital Status",
      employment_status ~ "Employment Status",
      region ~ "Region",
      health_insurance ~ "Health Insurance",
      medication ~ "On Medication",
      visits_last_year ~ "Visits Last Year",
      satisfaction ~ "Health Satisfaction (1-5)"
    )
  ) %>%
  add_n() %>%
  modify_header(label = "**Characteristic**", estimate = "**Mean (SD) or N (%)**") %>%
  modify_table_styling(columns = everything()) %>%
  add_overall()  # This adds an overall column
```

### gt_save PDF

```{r eval = FALSE}
gt::gtsave(as_gt(summary_table), filename = "outputs/pdf/too_wide_gt_pdf.pdf")
```

[Preview the Output](outputs/pdf/too_wide_gt_pdf.pdf)

- table cut off at the end of the page (portrait)

### rmarkdown rendered PDF

```{r eval = FALSE}
summary_table
```

[Preview the Output](outputs/pdf/too_wide_rmd_pdf.pdf)

- table cut off at the end of the page (portrait)

### gt_save rendered word file

```{r eval = FALSE}
gt::gtsave(as_gt(summary_table), filename = "outputs/docx/too_wide_gt_word.docx")
```

[Preview the Output](outputs/docx/too_wide_gt_word.docx)
- table condensed (squished) to fit on the page (text wrapping within cells)

### quarto rendered word file

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/docx/too_wide_qmd_word.docx)
- table condensed (squished) to fit on the page (text wrapping within cells)


### rmarkdown rendered word file

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/docx/too_wide_rmd_word.docx)

- table condensed (squished) to fit on the page (text wrapping within cells)
