---
title: "Setting Column Widths"
format: html
editor: visual
---

## Adjusting column Widths output

Default column width (no manipulation)
```{r eval=T}

library(gtsummary)
tbl <- gtsummary::tbl_summary(gtsummary::trial, by = trt, include = c(age, grade), missing = "always", label = list(age = "Age")) |> add_overall()
  
tbl
```

Using the `pct()` function within the `col_widths()` function from the {gt} package.
```{r}

tbl <- tbl |>
  as_gt()|>
  gt::cols_width(
        contains("label") ~ pct(70),
        everything() ~ pct(30))
tbl

```

### gt_save PDF

```{r, eval=FALSE}
gt::gtsave(tbl, filename = "outputs/pdf/col_widths_gt_pdf.pdf")
```

[Preview the Output](outputs/pdf/col_widths_gt_pdf.pdf)
- column width applied, all cols fit on page

### rmarkdown rendered PDF

```{r eval = FALSE}
tbl
```

[Preview the Output](outputs/pdf/col_widths_rmd_pdf.pdf)
- column width applied, table cut off after 1 col

### quarto rendered PDF

```{r eval = FALSE}
tbl
```

[Preview the Output](outputs/pdf/col_widths_qmd_pdf.pdf)
- column width applied, table cut off after 1 col

### gt_save rendered word file

```{r eval = FALSE}
gt::gtsave(tbl, filename = "outputs/docx/col_widths_gt_word.docx")
```

[Preview the Output](outputs/docx/col_widths_gt_word.docx)
- new column width isn't applied

### quarto rendered word file

```{r eval = FALSE}
tbl
```

[Preview the Output](outputs/docx/col_widths_qmd_word.docx)
- new column width isn't applied


### rmarkdown rendered word file

```{r eval = FALSE}
tbl
```

[Preview the Output](outputs/docx/col_widths_rmd_word.docx)
- new column width isn't applied

