---
title: "Setting Column Widths"
format: html
editor: visual
---

## Adjusting column Widths output


```{r eval=FALSE}

library(gtsummary)
tbl <- gtsummary::tbl_summary(gtsummary::trial, by = trt, include = c(age, grade), missing = "always", label = list(age = "Age  \n\U00A0\U00A0linebreak in a cell")) |> add_overall()
gt_table <- tbl$table_body |> 
  gt::gt(caption = gt::md("This is the caption  \n[Used for cross referencing in Quarto]")) |> 
  gt::fmt_markdown(columns = label) |> # need this to recognize the line break in the table body
  # Column headers with line breaks
  gt::cols_label(
    stat_0 = gt::md("**Overall**"),
    stat_1 = gt::md("**Drug A**  \nManual Line Break"), 
    stat_2 = gt::md("**Drug B**  \nManual Line Break")
  ) |> 
  gt::tab_header(gt::md("This is the Title  \nwith a linebreak"), subtitle = "This is the Subtitle") |>
  gt::cols_width(everything() ~ px(200)) #apply a 200 px width to all columns
```

### gt_save PDF

```{r}
gt::gtsave(gt_table, filename = "outputs/pdf/col_widths_gt_pdf.pdf")
```

[Preview the Output](outputs/pdf/col_widths_gt_pdf.pdf)
- column width applied but the table is cut off if it doesn't fit in the page

### rmarkdown rendered PDF

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/pdf/col_widths_rmd_pdf.pdf)
- column width applied but the table is cut off if it doesn't fit in the page

### quarto rendered PDF

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/pdf/col_widths_qmd_pdf.pdf)
- column width applied but the table is cut off if it doesn't fit in the page

### gt_save rendered word file

```{r eval = FALSE}
gt::gtsave(gt_table, filename = "outputs/docx/col_widths_gt_word.docx")
```

[Preview the Output](outputs/docx/col_widths_gt_word.docx)
- new column width isn't applied

### quarto rendered word file

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/docx/col_widths_qmd_word.docx)
- new column width isn't applied


### rmarkdown rendered word file

```{r eval = FALSE}
gt_table
```

[Preview the Output](outputs/docx/col_widths_rmd_word.docx)
- new column width isn't applied

